---
title: "Crosstalk"
author: "Angela Zoss"
date: "4/16/2021"
output: html_document
---

Crosstalk is a package that allows packages that create html-based widgets to talk to each other in an R Markdown document. Examples of HTML widgets include interactive charts, maps, and data tables. Crosstalk connects these components to each other by having them pull from a shared dataset. Crosstalk also offers a few interactive filter functions. For basic data exploration, Crosstalk may offer an easier alternative than Shiny, and the output of Crosstalk is simple HTML, which does not require a special server for sharing like Shiny apps do.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, echo=FALSE)
```

```{r library}

library(tidyverse)
library(lubridate)
library(DT)
library(plotly)
library(crosstalk)

```

```{r data}

# from https://github.com/emonson/pandas-datamatters 
# and https://github.com/emonson/pandas-jupyterlab

nc_no2_hourly <-  read_csv("https://raw.githubusercontent.com/emonson/pandas-datamatters/main/data/NC_NO2_hourly_2018.csv") %>%
  mutate(timestamp = ymd(`Date Local`) + hms(`Time Local`))

no2_daily <- nc_no2_hourly %>%
  #dplyr::filter(`County Name` == "Forsyth") %>%
  group_by(`Date Local`, `County Name`) %>%
  summarise(mean_measurement = mean(`Sample Measurement`, na.rm=T))

# Wrap data frame in SharedData
shared_daily <- SharedData$new(no2_daily)

```

```{r crosstalk}

bscols(
  list(
    bscols(filter_slider("dates", "Date Range", shared_daily, column=~`Date Local`, step=1, width=250),
    filter_select("county", "County", shared_daily, group=~`County Name`)),
    plot_ly(shared_daily, x=~`Date Local`, y=~`mean_measurement`, name='Forsyth', type = 'scatter'),
    DT::datatable(shared_daily, 
              filter = 'top', 
              options = list(
                dom = 'ltip'
                )
              )
  )
)  

  

```

