---
title: "DT"
author: "Angela Zoss"
date: "4/16/2021"
output: html_document
---

DT is a package that displays data frames in a user-friendly way. It works especially well inside R Markdown documents, which can incorporate "HTML widgets," or little chunks of website that get built from the R script, incorporating datasets and analyses in really interesting ways.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

```{r library, echo=FALSE}

library(tidyverse)
library(lubridate)
library(DT)

```

```{r data, echo=FALSE}

# from https://github.com/emonson/pandas-datamatters 
# and https://github.com/emonson/pandas-jupyterlab

nc_no2_hourly <-  read_csv("https://raw.githubusercontent.com/emonson/pandas-datamatters/main/data/NC_NO2_hourly_2018.csv") %>%
  mutate(timestamp = ymd(`Date Local`) + hms(`Time Local`))

no2_head <- head(nc_no2_hourly, n=1000)

```

## Default DT output

```{r default}

DT::datatable(no2_head)

```

## Changing DT style with classes

```{r styled}

DT::datatable(no2_head, class = 'cell-border stripe')

```

## Changing additional defaults

```{r change-defaults}

DT::datatable(no2_head, options = list(
  pageLength = 5,
  lengthMenu = c(5, 10, 15, 20)
))

```

## Adding column filters

```{r column-filters}

DT::datatable(no2_head, 
              filter = 'top', 
              options = list(
  pageLength = 5,
  lengthMenu = c(5, 10, 15, 20)
))

```

## Turning off global search

```{r no-search}

# see DOM options at https://datatables.net/reference/option/dom

DT::datatable(no2_head, 
              filter = 'top', 
              options = list(
  pageLength = 5,
  lengthMenu = c(5, 10, 15, 20),
  dom = 'ltip'
))

```
