---
title: "Flexdashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(DT)
library(plotly)
library(crosstalk)

# from https://github.com/emonson/pandas-datamatters 
# and https://github.com/emonson/pandas-jupyterlab

nc_no2_hourly <-  read_csv("https://raw.githubusercontent.com/emonson/pandas-datamatters/main/data/NC_NO2_hourly_2018.csv") %>%
  mutate(timestamp = ymd(`Date Local`) + hms(`Time Local`))

no2_daily <- nc_no2_hourly %>%
  #dplyr::filter(`County Name` == "Forsyth") %>%
  group_by(`Date Local`, `County Name`) %>%
  summarise(mean_measurement = mean(`Sample Measurement`, na.rm=T))

# Wrap data frame in SharedData
shared_daily <- SharedData$new(no2_daily)

```

<!-- check out https://matt-dray.github.io/earl18-crosstalk/04_leaflet-flexdash-dt-crosstalk.html -->

Inputs {.sidebar}
-----------------------------------------------------------------------

### Set Your Filters

```{r}
filter_slider("dates", "Date Range", shared_daily, column=~`Date Local`, step=1)

filter_select("county", "County", shared_daily, group=~`County Name`)

```

Row
-----------------------------------------------------------------------

### {data-width=650}
    
```{r}

plot_ly(shared_daily, x=~`Date Local`, y=~`mean_measurement`, name='Forsyth', type = 'scatter')

```

### About flexdashboard {data-width=350}

Flexdashboard is a library that takes R Markdown documents and turns them into a website. You can build up different website layout elements like pages, panels, rows, and columns. In each part of your website, you can use a blend of text/image content and R code, just like in normal R Markdown documents. A flexdashboard document can be compiled (or "knit") to an HTML file that can then be shared as a file or published as a website.

Row
-----------------------------------------------------------------------

### {}
    
```{r}

DT::datatable(shared_daily, 
              filter = 'top', 
              options = list(
                dom = 'ltip'
                )
              )

```
   